Model validation plots

### 2021-06-14 doc/paper.Rmd
only load targets when needed. (#64)

```{r load-targets}
withr::with_dir(here::here(), {
  tar_load(c(
    eda_plot,
    surv_curve,
    s_spei_plot,
    g_spei_plot,
    f_spei_plot,
    size_plot,
    f_cf,
    f_1ha,
    model_data,
    xa_spei
  ))
})
```

@@

```{r flwr-prob-quartile, include=FALSE}

#figure out flowering probability of largest quartile of plants in each habitat
library(tidyverse)
newdf_cf <-
  f_cf$model %>% #use model data frame
  mutate(quartiles = ntile(log_size_prev, 4)) %>% 
  filter(quartiles == 4)

newdf_1ha <-
  f_1ha$model %>% 
  mutate(quartiles = ntile(log_size_prev, 4)) %>% 
  filter(quartiles == 4)

#equivalent to flowering once every __ years
1/predict(f_cf, newdata = newdf_cf) %>% mean() %>% plogis()
1/predict(f_1ha, newdata = newdf_1ha) %>% mean() %>% plogis()
```

@@

```{r eda, fig.cap=eda_cap, fig.width=7, fig.height=7}
eda_plot & theme(text = element_text(size = 10))
```

@@

```{r surv-curve, fig.cap=surv_curve_cap, fig.width=7, fig.height=3.5}
surv_curve + theme(text = element_text(size = 10))
```

@@

```{r size-plot, fig.cap=size_cap, fig.width=7, fig.height=7}
# size_plot & theme(text = element_text(size = 10))
include_graphics(here("doc", "figures", "size_plot_ufhpc.png"))
```

@@

```{r surv-spei, fig.cap=s_spei_cap, fig.height=7.5, fig.width=7}
s_spei_plot & theme(text = element_text(size = 10))
```

@@

```{r growth-spei, fig.cap=g_spei_cap, fig.height=7.5, fig.width=7}
g_spei_plot & theme(text = element_text(size = 10))
```

@@

```{r flwr-spei, fig.cap=f_spei_cap, fig.height=7.5, fig.width=7}
# f_spei_plot & theme(text = element_text(size = 10))
include_graphics(here("doc", "figures", "f_spei_plot_ufhpc.png"))
```

>>>>

```{r load-targets}
withr::with_dir(here::here(), {
  tar_load(c(
    # eda_plot,
    # surv_curve,
    # s_spei_plot,
    # g_spei_plot,
    # f_spei_plot,
    # size_plot,
    model_data,
    xa_spei
  ))
})
```

@@

@@

```{r eda, fig.cap=eda_cap, fig.width=7, fig.height=7}
tar_read(eda_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-curve, fig.cap=surv_curve_cap, fig.width=7, fig.height=3.5}
tar_read(surv_curve) + theme(text = element_text(size = 10))
```

@@

```{r size-plot, fig.cap=size_cap, fig.width=7, fig.height=7}
tar_read(size_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-spei, fig.cap=s_spei_cap, fig.height=7.5, fig.width=7}
tar_read(s_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r growth-spei, fig.cap=g_spei_cap, fig.height=7.5, fig.width=7}
tar_read(g_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r flwr-spei, fig.cap=f_spei_cap, fig.height=7.5, fig.width=7}
tar_read(f_spei_plot) & theme(text = element_text(size = 10))
```

### 2021-06-14 doc/validate_models.Rmd
only load targets when needed. (#64)

```{r load-targets}
withr::with_dir(here::here(),{
  tar_load(c(
    s_cf,
    s_1ha,
    g_cf,
    g_1ha,
    f_cf,
    f_1ha,
    s_cf_sub,
    g_cf_sub,
    f_cf_sub
    ))
  })
```

@@

Quantile residuals are more appropriate for binomial models.
### Fragments

```{r}
summary(s_1ha)
```

@@

```{r}
draw(s_cf_sub)
```
Surface still looks different in a similar way though.

@@

@@

@@

@@

>>>>

@@

Quantile residuals are more appropriate for binomial models.
### Fragments
```{r}
withr::with_dir(here::here(),{
  tar_load(c(s_1ha, s_cf, s_cf_sub))
})
```

```{r}

summary(s_1ha)
```

@@

```{r}
draw(s_cf_sub)
```
Surface still looks different in a similar way though.
```{r}
rm(s_1ha, s_cf, s_cf_sub)
```

@@

```{r}
withr::with_dir(here::here(),{
  tar_load(c(g_1ha, g_cf, g_cf_sub))
})
```

@@

```{r}
rm(g_1ha, g_cf, g_cf_sub)
```

@@

```{r}
withr::with_dir(here::here(),{
  tar_load(c(f_1ha, f_cf, f_cf_sub))
})
```

@@

### Flowering prob of largest plants

Figure out flowering probability of largest quartile of plants in each habitat

```{r}
newdf_cf <-
  f_cf$model %>% #use model data frame
  mutate(quartiles = ntile(log_size_prev, 4)) %>% 
  filter(quartiles == 4)

newdf_1ha <-
  f_1ha$model %>% 
  mutate(quartiles = ntile(log_size_prev, 4)) %>% 
  filter(quartiles == 4)
```

```{r}
#equivalent to flowering once every __ years
1/predict(f_cf, newdata = newdf_cf) %>% mean() %>% plogis()
1/predict(f_1ha, newdata = newdf_1ha) %>% mean() %>% plogis()
```

```{r}
rm(f_1ha, f_cf, f_cf_sub)
```
